Supplemental Information A: Full Annotated Analysis and Reproducible Code

### 2022-09-18 Supplemental-Material-A-Annotated-Analysis.Rmd
Update Supplemental-Material-A-Annotated-Analysis.Rmd

```{=html}
<style type="text/css">
.main-container {
  max-width: 1300px;
  margin-left: auto;
  margin-right: auto;
}
.table {
  margin-left:auto; 
  margin-right:auto;
}
</style>
```
```{r setup, include=FALSE}
# R Studio Clean-Up
cat("\014") # clear console
# rm(list=ls()) # clear workspace - use restart R instead [cmd/alt + shift + F10]
gc() # garbage collector

@@

#################################################################
##               EXPORT FOR STM MACHINE LEARNING               ##
#################################################################
# bannerCommenter::banner("EXPORT FOR STM MACHINE LEARNING", centre = TRUE, bandChar = "#")
# varNamPosAdd <- c("relatedness", "autonomy", "competence")
# 
# dtAllStm <- rbind(
#   dtS1$full %>% select(KeyNeed, DaytimeNeed, any_of(varNamS123MiRed), any_of(varNamPosAdd)) %>% mutate(study = "S1") %>%
#     mutate(across(!TID & !study & !KeyNeed & !DaytimeNeed, as.numeric)),
#   dtS2$full %>% select(KeyNeed, DaytimeNeed, any_of(varNamS123MiRed), any_of(varNamPosAdd)) %>% mutate(study = "S2"),
#   dtS3$full %>% select(KeyNeed, DaytimeNeed, any_of(varNamS123MiRed), any_of(varNamPosAdd)) %>% mutate(study = "S3")
# ) %>%
#   group_by(study, PID) %>%
#   mutate(ID = cur_group_id()) %>%
#   ungroup %>%
#   mutate(
#     date = as.Date(gsub(" .*", "", TID)),
#     week = strftime(date, format = "%Y-W%V")
#   ) %>%
#   select(ID,
#          PID,
#          study,
#          TID,
#          TIDnum,
#          date,
#          week,
#          IntergroupContact,
#          IngroupContact,
#          everything(),
#          -starts_with("ResponseId")) %>%
#   as.data.frame
# 
# dtAllStm2 <- dtAllStm
# 
# dtAllStm2$IntGrAnx.pre_calc <-
#   psych::scoreItems(
#     keys = c(rep(1,6),rep(-1,6)),
#     items = dtAllStm2 %>% select(matches("^IntGrAnx[0-9]{2}.?\\.pre")),
#     min = 1,
#     max = 10
#   )$scores %>%
#   as.numeric
# 
# dtAllStm2$IntGrAnx.post_calc <-
#   psych::scoreItems(
#     keys = c(rep(1,6),rep(-1,6)),
#     items = dtAllStm2 %>% select(matches("^IntGrAnx[0-9]{2}.?\\.post")),
#     min = 1,
#     max = 10
#   )$scores %>%
#   as.numeric
# 
# dtAllStm2$swl.pre_calc <-
#   psych::scoreItems(
#     keys = rep(1,5),
#     items = dtAllStm2 %>% select(matches("^SWL[0-9]{2}\\.pre")),
#     min = 1,
#     max = 7,
#     missing = TRUE,
#     impute = "none",
#   )$scores %>%
#   as.numeric
# 
# dtAllStm2$discrimination.post_calc <-
#   psych::scoreItems(
#     keys = rep(1,9),
#     items = dtAllStm2 %>% select(matches("^EvDayDiscr[0-9]{2}\\.post")),
#     min = 1,
#     max = 6,
#     missing = TRUE,
#     impute = "none",
#   )$scores %>%
#   as.numeric
# 
# dtAllStm3 <- dtAllStm2 %>%
#   select(
#     -matches("^IntGrAnx[0-9]{2}.?\\.pre"),
#     -matches("^IntGrAnx[0-9]{2}.?\\.post"),
#     -matches("^SWL[0-9]{2}\\.pre"),
#     -matches("^EvDayDiscr[0-9]{2}\\.post"),
#     -relatednessSelf,
#     -relatednessOther,
#     -relatednessNoInteraction
#   )
# 
# write.csv2(dtAllStm3,
#            file = "data/keyMotivesSTM.csv")
#################################################################

@@

>>>>

```{=html}
<style type="text/css">
.main-container {
  max-width: 1300px;
  margin-left: auto;
  margin-right: auto;
}
.table {
  margin-left:auto; 
  margin-right:auto;
}
</style>
```

```{r setup, include=FALSE}
# R Studio Clean-Up
cat("\014") # clear console
# rm(list=ls()) # clear workspace - use restart R instead [cmd/alt + shift + F10]
gc() # garbage collector

@@

@@

```{r s2StlTest}
# Seasonal Decomposition of Time Series by Loess

dtMiS2 %>% 
  select(
    PID,
    TIDnum,
    AttitudesDutch
  ) %>%
  #filter(PID == 1) %>%
  #na.exclude(as.ts(.)) %>%
  as.ts %>%
  stats::stl(., na.action=na.omit)

testLoess <- loess(AttitudesDutch ~ TIDnum, data = dtMiS2 %>% filter(PID == 1))
testSpline <- pspline::sm.spline(dtMiS2$AttitudesDutch, dtMiS2$TIDnum)
testMarkov <- semiMarkov()

stats::stl(dtMiS2Fin)
